He-Man: A domain-specific language for lightweight concurrency

### 2012-03-08 paper/paper.tex
Minor fixes

@@

As an example of the power that Haskell and the monadic style gives
us, Figure \ref{fig:generic} shows our library routines for simulating
blocking network operations. \t{do\_nb\_action} takes an event
\t{Expr} and a \t{Prog Expr} action representing a network call that
can return \t{EAGAIN} and produces an action that generates code to
simulate a blocking network operation. This allows us to describe how
to simulate blocking I/O in a generic way, and then invoke it to
create our concrete wrappers. (\t{.=.} is a wrapper for \b{Assign} 
that takes a \t{Prog Expr} as its second argument and the \t{sock\_*} 
functions invoke \b{Call} wrappers on the appropriate network calls.)

@@

\begin{figure}[ht]
\centering
\begin{code}
child_code = declare_thread (Int) $
  \[child_fd] -> do
  ev <- setup_connection child_fd
  buf <- new_buf bufsize
  while 1 $ do
    amt_read <- do_read ev buf bufsize
    ifthen (amt_read .== 0) exit
    amt_written <- full_write ev buf amt_read
    ifthen (amt_written .< amt_read) exit
\end{code}
\caption{He-Man example from echo server.}
\label{fig:code-ex}
\end{figure}

>>>>

% XXX: We need to cite ElliottEtAl somewhere!

@@

As an example of the power that Haskell and the monadic style gives
us, Figure \ref{fig:generic} shows our library routines for simulating
blocking network operations. \t{do\_nb\_action} takes an
\t{Expr} and a \t{Prog IntE} action representing a network call that
can return \t{EAGAIN} and produces an action that generates code to
simulate a blocking network operation. This allows us to describe how
to simulate blocking I/O in a generic way, and then invoke it to
create our concrete wrappers. (\t{.=.} is a wrapper for \b{Assign} 
that takes a \t{Prog Expr} as its second argument and the \t{sock\_*} 
functions invoke \b{Call} wrappers on the appropriate network calls.)

@@

\begin{figure}[ht]
\centering
\begin{code}
child_code = declare_thread (Int) $
  \child_fd -> do
  ev <- setup_connection child_fd
  buf <- new_buf bufsize
  while 1 $ do
    amt_read <- do_read ev buf bufsize
    ifthen (amt_read .== 0) exit
    amt_written <- full_write ev buf amt_read
    ifthen (amt_written .< amt_read) exit
\end{code}
\caption{He-Man example from echo server.}
\label{fig:code-ex}
\end{figure}
